\section{Project Management and Collaboration Plan}
\label{sec:collab}

We first describe the leadership team, including their primary roles
on the project.  This is followed by a description of our approach
to collaboration and a timeline for the research activities.

{\bf Roger D. Chamberlain}, PI, is Professor of Computer Science
and Engineering in the School of Engineering and Applied Science
at Washington University in St.~Louis.
Prof.~Chamberlain will have overall responsibility for managing the
research project and will take the lead in development of Markov
decision process models, performance evaluation, and electrical engineering
design requirements.

{\bf Chandler Ahrens}, Co-PI, is Assoc.~Professor of Architecture
in the Sam Fox School of Design \& Visual Arts
at Washington University in St.~Louis.
Prof.~Ahrens will take the lead in the physical design aspects of
the catoptric surfaces, including their shape, configuration, positioning,
fabrication, and installation.

{\bf Chris D. Gill}, Co-PI, is Professor of Computer Science
and Engineering in the School of Engineering and Applied Science
at Washington University in St.~Louis.
Prof.~Gill will lead the software development efforts, with an emphasis
on designing for reuse whenever reasonable.  He will also lead our
approach to reusable abstractions that can be generalized to other
cyber-physical system uses.

All three faculty have worked together in the past, so the organization
of the present collaboration will be straightforward.  Co-authored
publications with two more of the faculty
include~\cite{cag18,mgc16, mskgct13}. Ahrens and Chamberlain collaborated
on the design and implementation of the catoptric surface being
installed in Steinberg Hall, and Chamberlain and Gill have previously
co-advised a doctoral student (J.~Meier, currently at Lockheed Martin)
who exploited Markov decision processes for RF spectrum management.

We will exploit the fact that the entire team is located on the
Danforth Campus of Washington University in St. Louis to organize
our collaboration around face-to-face meetings.  Our weekly meetings will
form the backbone of the collaboration, where we check in each other to
update status, plan next steps, and address any issues that have arisen
since our previous meeting.
We will also gather for the purpose of reviewing the literature
(traditional journal club activities), student presentations (frequently
practice talks for upcoming conference presentations), and reports
to the group from anyone who has recently returned from a conference trip.

Our initial plan for the project timeline is listed below, indicating the
primary activities to be pursued in each year of the project.

\subsection*{Year 1}

\begin{itemize}

\item Perform quantitative measurements on Steinberg catoptric surface.

\item Design initial MDPs, incorporating daylighting and heat harvesting.

\item Develop initial abstractions for low-level controller software.

\item Evaluate imaging approach for positioning feedback.

\item Perform initial design work for VelociData installation.

\item Submit human subjects evaluation plan to IRB for approval.

\end{itemize}

\subsection*{Year 2}

\begin{itemize}

\item Decommission Steinberg surface and re-purpose components for
reliability testing.

\item Expand MDPs to include additional constraints (i.e., to ensure
safety).

\item Develop initial abstractions for MDP-based optimization software.

\item Install VelociData catoptric surface and perform empirical evaluation.

\item Perform quality of experience evaluation for VelociData users.

\item Perform initial design work for BECS installation.

\end{itemize}

\subsection*{Year 3}

\begin{itemize}

\item Expand MDPs to include additional goals (e.g., to prioritize
reliability).

\item Install BECS catoptric surface and perform empirical evaluation.

\item Perform quality of experience evaluation for BECS users.

\item Refine software abstractions for both low-level positioning control
and high-level MDP-based optimization, based upon what has been learned
from earlier editions.

\item Release software under open source licensing terms.

\end{itemize}
