\section{Evaluation/Experimentation Plan}
\label{sec:eval}

We will organize our experimentation and evaluation activities around
three prototype catoptric surfaces.  The first is the system currently
being installed in the south window of Steinberg Hall's atrium (described
in Section~\ref{sec:background}).
The second will be designed for and installed at VelociData, Inc.,
a startup firm in
St.~Louis that is located in the recently announced \emph{39~North}
innovation district.
The third will be designed for an installed at BECS Technology, Inc.,
a local manufacturer of electronic control systems that has recently
relocated to a newly redeveloped 42,000~sq.~ft. facility. 
This is followed by a discussion of our software development
and assessment plans.

\subsection{Steinberg Hall, Washington University in St. Louis}

Steinberg Hall is situated on the Danforth Campus of Washington University
in St.~Louis. It is one of the buildings that houses the College
of Architecture, and is within easy walking distance of the Dept. of
Computer Science and Engineering.

The catoptric surface that is being installed at the south end of the
atrium will be complete by the start date of the proposed research project.
We will use it for a number of purposes:
\begin{enumerate}

\item Development and calibration of quantitative daylight delivery models.
We will evaluate the effectiveness of our current ray-tracing software
system in assessing the impact of different configurations of the surface
(i.e., various mirror positions).  Empirical evaluation will use a number
of light meters distributed within the space. The data collected will be
compared to our predictions as well as the analytical models
of both Bueno et al.~\cite{bwkk15} and Galatioto and Beccali~\cite{gb16}.

\item Practical aspects.
We will learn several practical things from this installation, including
the positioning precision achievable with our current physical design, the
viability of operating the mirror positioning motors open loop (the pan-tilt
is stepper motor driven and the current system does not incorporate
shaft encoders or other positioning feedback), etc.

\item Investigation of the ability to provide positioning feedback via
image analysis.  We will install a camera with the full surface in its
field of view and assess the viability of using image analysis techniques
to discern the orientation of each mirror.  An imporant component of this
will be the degree of precision that is achievable.

\item Quantification of the viable heat transfer.
We will perform a controlled experiment in which we will focus varying
amounts of sunlight on a vessel of water to determine the temperature
rise that is achievable.  This will enable us to calibrate heat transfer
models that will go into the MDP formulation.

\item Reliability testing of the components.
This installation is not permanent. When it is decommissioned, we will
setup a representative collection of the mirror components in our laboratory
for stress testing (to failure).  This will allow us to calibrate our
reliability models for inclusion in the MDPs.

\end{enumerate}

\subsection{VelociData, Inc., 39 North Innovation District}

VelociData, Inc., is located at 10425 Old Olive Stree Rd., St.~Louis, MO.
They are in the \emph{39 North}
innovation district, which has the Danforth
Plant Science Center, Monsanto, Bio Research \& Development Growth Park,
and Heliz Center Biotech Incubator as anchors. It is a 10~min.~drive from
the Washington University Danforth Campus, and they have given us
permission to install a prototype at their facility (see letter
of collaboration).

There are a pair of potential installation sites at VelociData's location.
An east-facing window provides light to an individual's office, and
(the more interesting option) a west-facing window provides light to
a bullpen of cubicles that are occupied by design engineers.

As we will not be able to tie into the HVAC system at this location, our
objectives will be focused on the daylighting benefits, including their
impact on the occupants of the space\footnote{All experimentation that
includes human subjects will undergo review by the Washington University
IRB prior to implementation.}.

We will use this installation for the following purposes:

\begin{enumerate}

\item Assess utility of non-southern facing windows.
Since the windows at VelociData's location are on the top floor, and face
either east or west, this gives us the opportunity to explore the viability
of exploiting multiple-reflection designs
(e.g., a fixed position mirror above the
roofline that redirects sunlight to the active catoptric surface).

\item Evaluate human response.
While we do not have the budget in this project to perform
comprehensive productivity analyses, we will be in a position to
query the building occupants about their experience with the
daylight effects. E.g., do they see value in the controllability
of the quantity of daylight?

\item \FIXME{What else should we do at this site?}

\end{enumerate}

\subsection{BECS Technology, Inc., St. Louis County}

BECS Technology, Inc., is located at
10818~Midwest Industrial Dr., St.~Louis, MO.
They are a small manufacturer of electronic control
systems for a number of markets (e.g., agriculture, aquatics, refrigeration).
The unique benefit to this installation is that they have agreed to
allow us to have access to the HVAC system in their building (see letter
of collaboration).

\FIXME{Describe HVAC system at BECS, and how we will tie in.}

We will use this installation for the following purposes:

\begin{enumerate}

\item Repeat assessments from initial installations.
As each installation will have a unique configuration, we will exploit the
latter two installations (at VelociData and BECS) to perform common
experiments at each, comparing the results to increase the confidence
in any conclusions that we draw based on empirical data.
This will include all of the calibration efforts, as well as the comparison
of empirical data to the theoretical models (both for daylight delivery
and thermal heat transfer).
This will also include any human evaluations that are undertaken at
the VelociData site.

\item Integration into the HVAC system.
\FIXME{Describe this.}

\item Assessment of manufacturability.
As described in the Transfer to Practice Supplementary Document, BECS
is planning to assist us in evaluating the commercial viability of the
catoptric surface as a product.  An important piece of this evaluation is
the assessment (by design and manufacturing engineers at BECS) of the
manufacturability of the system.

\item \FIXME{What else here?}

\end{enumerate}

\subsection{Software Development and Assessment}

\FIXME{What should go here?}
