\documentclass[11pt]{article}
\usepackage{epsfig}
\usepackage{subfig}
\usepackage{setspace}
\usepackage{url}
\usepackage{colortbl} 
\usepackage{comment} 

\setlength{\textheight}{8.875in} \setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0.0in} \setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in} \setlength{\oddsidemargin}{0.0in}

%for comments
\newcommand{\FIXME}[1]{\textcolor{red}{FIXME: #1}}

\begin{document}
\pagestyle{plain}
\thispagestyle{plain}

\begin{center}
\textbf{\Large Transition to Practice}
\end{center}

In what follows, we describe the transition to practice option for the
research proposal.  We start with an articulation of the specific goals
of the transition to practice, and follow that with a discussion of the
execution plan.  We conclude with the budget estimate.

\section{TTP Goals}

Specific goals we wish to accomplish as part of our transition to practice
include the following.

\begin{enumerate}

\item \emph{Revise the design of the catoptric surface so that it can
be installed outside.}

Our initial two surfaces (already in place),
and those that we will construct as part of the research plan,
are all intended for indoor installation (e.g., in an atrium
or on or near a window.  This simplifies the design in a number of ways,
primarily enabling us to focus on the physical motion of the mirrors, without
having to ensure that each component is also weatherproof.

If the the system can be installed outside, that significantly increases
the circumstances under which it can be used practically.
When the mirror units can be located outside, then they are able to
be exposed to daylight beyond any obstructions such as roof overhangs.
An overhang can block some of the high altitude angle sunlight during
summer months or in locations near the equator.
An additional benefit is that the mirror units can provide some
shading for the interior area just inside the window.
This could benefit interior spaces in two ways.
First, the solar heat gain on the floor or desks near a window
may be unwanted and the mirror units can direct the daylight to
where it is more useful.
Second, direct daylight can cause too much luminous intensity or
glare in the area around the window and our systems can redirect
the light to bounce off the ceiling to diffuse the light before
reaching the task height of the occupants. 

\item \emph{Design and implement a user-friendly interface to the
open source software.}

As part of the research plan, we intend to design and implement two
levels of control software (one, low-level positioning control for a
pan-tilt physical system, and two, high-level management software for
Markov decision process optimization).  All of this software will be
released with an open source distribution.

However, during the research phase, the user interfaces to this software
will not be the primary focus of our effort.  As part of the transition
to practice, we will design and build an appropriate user interface that
enables the architecture community to both use each component individually
and to integrate them seamlessly.  This user interface capability will
also be released under an open source license.

\item \emph{Investigate the commercialization options for the system.}

We will explore two paths to assessing the potential for commercialization
of catoptric systems.
First, we will ask a number of practicing architects to evaluate the
catroptic surface and provide us with their professional opinions
(see letters).
Second, we will work with the manufacturing firm that is our second
prototype installation site, BECS Technology, to assess the commercial
viability from the point of view of a manufacturer (see letter).

Our group has significant experience in commercialization efforts.
PI R.~Chamberlain has formed 4 companies over the course of his professional
career, 3 of which are still in operation and collectively employ
over 200 individuals in St.~Louis, Chicago, New York, and London, UK.
Co-PI C.~Ahrens is a licensed architect with 22 years of professional
experience, working on institutional, commercial, and residential
buildings that focus on sustainable fa\c{c}ade and mechanical systems.
The projects have been located around the world in Europe, the Middle East,
China and the United States. As an example, he was the main designer for
the engineering building for Cooper Union, which was the first
LEED Platinum rated laboratory building in the United States.
Many of his completed buildings have won numerous awards for their
sustainable technologies.
He is currently the owner of an architecture firm and continues
to employ sustainable technologies and techniques in his practice.  
Co-PI C.~Gill has worked extensively with industry partners throughout his
research career, including developing software in collaboration with Boeing, 
BBN Technologies, and Honeywell that was used in manned flight demonstrations.

\end{enumerate}

\section{TTP Plan}

The duration of the transition to practice plan will be for 3 years.
The first two years will overlap with the primary research plan (and
are labeled years~2 and~3 in what follows).  The third year will extend
beyond the primary research plan and is labeled year~4.

\subsection*{Year 2}

\begin{itemize}

\item Design, prototype, and test several mirror elements aimed at
outdoor installation. This will include protection of the metallic components,
electronic components, and stepper motors.  The assessment will include
both the degree to which they can withstand the elements and whether or
not there is any degredation in operational peformance (e.g., reduced
positioning accuracy or other limitation).

\item Perform initial user interface design for individual software components.
For both the pan-tilt positioning control software and the MDP optimization
software, we will develop visualizations of the state of the system.
For the positioning control software, this will include a visual representation
of the physical surface and the current positioning of each mirror
(either as a whole system or a zoom-in option for a subset of the mirrors).
For the MDP optimization software, we will explore various graphical
representations that enable the user to easily comprehend the state
space, $\mathcal{X}$, of the MDP.

\end{itemize}

\subsection*{Year 3}

\begin{itemize}

\item Assess manufacturability of physical system.  In collaboration with
the design engineers at BECS Technology, 
we will evaluate the ability and cost of manufacturing the catoptric
surfaces in moderate to large volumes.

\item Prototype component user interfaces. This will include the individual
interfaces for the pan-tilt positioning controller software
and for the high-level MDP model specification.
In addition, we will explore an initial design that will allow users
to specify the MDP models using a graphical interface.  In effect, can we
let them draw the visualization of the state space that is then presented
as part of the MDP evaluation output?

\end{itemize}

\subsection*{Year 4}

\begin{itemize}

\item Integrate unified user interface.
We will integrate both the MDP model specification software and the
pan-tilt control software with the Grasshopper plug-in to Rhino3D.
As a visual programming language, Grasshopper is considered by
the architecture community to be user friendly (i.e., it is both familiar
and in common use).

\FIXME{Say more here?}

\item Assess commercial viability. \FIXME{Interacting with architects.}

\item Seek commercial partners.
Ultimately, if this system is to be put into practice, we must interest
a manufacturing firm in making catoptric surfaces and architects in utilizing
catoptric surfaces either in new construction or as a renovation option.
As indicated above, as part of the project
we are collaborating with firms that are qualified to
do each of these things.

Clearly, we will explore the options for commercialization with these
organizations; however, we will not limit our investigation there.  A major
task towards the completion of the project will be to seek out additional
potential partners for a commercialization effort.

\end{itemize}

\section{TTP Supplemental Budget}

The execution of the TTP plan will extend the duration of the research
project for 1 year, and will involve the addition of one more individual
to the team.  Ed Richter, Professor of Practice in Electrical and Systems
Engineering, will join the team in years 2 through 4 and will have a
substantial role in executing the transition to practice activities.

\begin{comment}
\newpage
\begin{table}[h]
\centering
\begin{tabular}{l l r r r}
\ & & Year 2 & Year 3 & Year 4 \\ 
Personnel: & & & & \\
\ & Chamberlain & & & 16,587 \\ 
\ & Gill & & & 18,920 \\ 
\ & Ahrens & & & 10,634 \\ 
\ & Richter & 19,800 & 20,394 & 21,006 \\ 
\ & GRA (3) & & & 104,297 \\
\ & fringes & 4,752 & 4,895 & 16,155 \\ \\
Travel: & & & & 6,000 \\ \\
Supplies: & & & & 10,000 \\ \\
Total Direct: & & 24,552 & 25,289 & 203,559 \\
Indirect: & & 13,995 & 14,541 & 117,046 \\ \\
Total: & & 38,547 & 39,830 & 320,605 \\ \hline
\ & & & & 398,982
\end{tabular}
\end{table}

\subsection*{TTP Supplemental Budget Justification}

\subsubsection*{Personnel}
We request one month of support per year for PI Chamberlain and Co-PIs
Ahrens and Gill in year~4.
We request 20\% time per year for Professor of Practice Ed Richter
in years 2, 3, and 4.
We request support for three GRAs in year~4. Salaries are 
assumed to increase 3\%/year. 

\subsubsection*{Travel}
We request \$6000/year for senior personnel and student travel
to present our work at academic 
conferences and to attend the PI meetings.
This is based upon a plan for 4 individual trips
each year, with an expected cost of \$1500 per trip.
Candidate conferences include ACADIA, ICCPS, RTAS, etc.
We will also ensure that at least one PI/Co-PI is
at the annual PI meetings that are arranged by NSF. 

\subsubsection*{Materials and Supplies}
We request \$10,000/year for
miscellaneous components to both keep the experimental catoptric
infrastructure operational and to make alterations to it for
experimental purposes. This will
include additional computational components (e.g., microcontrollers, etc.)
as well as physical components (e.g., mirrors, structural elements, motors,
etc.).

\subsubsection*{Indirect costs}
Indirect costs are requested at Washington University's standard rate of
55.5\% of MTDC (starting 7/1/2018), 57\% of MTDC (starting 7/1/2019), and
57.5\% of MTDC (starting 7/1/2020).

\end{comment}

\end{document}
